error checking the LE decomp functions

### 2016-10-26 Code/error checking the LE decomp fxs.Rmd
more cod decomp changes
fixed error in how cod table was sorted

We also need data on the proportion of deaths within each age bracket due to each cause of death.
```{r data_cod_proportions}
cod.props <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/working_teaching_examples/auger_cod_proportions.csv")
names(cod.props)[3] <- "prop.QC"
names(cod.props)[4] <- "prop.CAD"
head(cod.props)
```

>>>>

We also need data on the proportion of deaths within each age bracket due to each cause of death.
```{r data_cod_proportions}
cod.props <- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/working_teaching_examples/auger_cod_proportions.csv")
names(cod.props)[3] <- "prop.QC"
names(cod.props)[4] <- "prop.CAD"
head(cod.props)
```
